deckard: A Declarative Tool for Machine Learning Robustness Evaluations

### 2025-12-19 paper.tex
Commit from GitHub Actions (Render R Markdown)

To avoid any ambiguity about contributions, we clarify that
\texttt{deckard} is a method and software system introduced in this
work. Although the implementation is publicly available on GitHub, the
modular design, configuration-driven framework, and experimental
methodology are original to this paper. While the prior works outlined
in the Usage Section can be fully reproduced with this software, this
paper is the first to present the system as a cohesive method, fully
specified, documented, and intended for broad reuse.

>>>>

To avoid any ambiguity about contributions, we clarify that
\texttt{deckard} is a method and software system introduced in this
work. Although the implementation is publicly available on GitHub, the
modular design, configuration-driven framework, and the breadth of
adversarial analysis is unique to this work. While the prior works
outlined in the Usage Section can be fully reproduced with this
software, this paper is the first to present the system as a cohesive
method, fully specified, documented, and intended for broad reuse.
